---
title: "Medical Record"
author: "Alan T. Arnholt"
date: "January 11, 2015"
output: html_document
---

First create a data frame for the Medical Record.
```{r label = setup, comment = NA}
MRDF <- data.frame(ID = c(255, 638, 956, 551, 980), kg = c(116, 86, 72, 63, 114), cm = c(172, 176, 157, 169, 163), ease = factor(c("Difficult", "Easy", "Difficult", "Easy", "Impossible"), levels = c("Easy", "Difficult","Impossible")), treatment = factor(c("Traditional Sitting", "Hamstring Stretch", "Traditional Sitting", "Hamstring Stretch", "Traditional Sitting")), oc = c(0, 0, 0, 2, 0))
MRDF
str(MRDF)
```

Here is the Table:

```{r comment = NA, echo = FALSE}
library(knitr)
kable(MRDF)
```

* `ID` is a unique patient identifier.
* `kg` numeric variable that records the weight of the parturient woman.
* `cm` numeric variable that records the height of the parturient woman.
* `ease` categorical variable (factor) with three levels Easy, Difficult, and Impossible.
* `treatment` categorical variable (factor)  with two levels Hamstring Stretch, and Traditional Sitting.
* `oc` numeric variable that record the number of obstructive contacts.